Making Sequential Programs Deterministic

### 2019-04-02 experiments.tex

\section{deflaker case study}
\begin{table}[]
    \begin{tabular}{|l|l|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664& det checker not found \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  Removed tests (Printing (HTTP's) Response.getstatus())\\ \hline
        togglz [19] issue \#223 & (use NonDex for debugging) \\ \hline
        togglz [20] issue \#240 &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{deflaker case study}
\begin{table}[]
    \begin{tabular}{|l|l|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664& det checker on test files \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  Removed tests (Printing (HTTP's) Response.getstatus())\\ \hline
        togglz [19] issue \#223 & build issue \\ \hline
        togglz [20] issue \#240 &  \\ \hline
    \end{tabular}
\end{table}
